Relict deciduous oaks show high resilience to drought despite the effect of land-use legacies

### 2018-11-12 man/figures/corr_plot_years.Rmd
correlation plots

library("grid")
library("gridExtra")
library("patchwork")
library("ggcorrplot")
library("stringr")
library("pander")
library("lemon")
library("viridis")
library("ggthemes")
```

@@

upper <- cor_rt 
upper[upper.tri(cor_rt, diag = TRUE)]<- ""
upper <- as.data.frame(upper)
upper

g_rt <- ggcorrplot(cor_rt, method = "circle", 
                   type='upper', ggtheme = theme_minimal,
                   lab=TRUE, title='BAI Rt', show.legend = FALSE, tl.cex = 14)

# https://briatte.github.io/ggcorr/

ggcorr(data = NULL, cor_matrix = cor_rt, geom = 'text', 
       label_size = 7, label_round = 2, legend.position = 'none')

g_rc <- ggcorrplot(cor_rc, type='upper', lab=TRUE, title='BAI Rc', show.legend = FALSE)
g_rs <- ggcorrplot(cor_rs, type='upper', lab=TRUE, title='BAI Rs', show.legend = FALSE)
g_rte <- ggcorrplot(cor_rte, type='upper', lab=TRUE, title='EVI Rt', show.legend = FALSE)
g_rce <- ggcorrplot(cor_rce, type='upper', lab=TRUE, title='EVI Rc', show.legend = FALSE)
g_rse <- ggcorrplot(cor_rse, type='upper', lab=TRUE, title='EVI Rs', show.legend = TRUE)

>>>>

library("grid")
library("GGally")
library("gridExtra")
library("patchwork")
library("ggcorrplot")
library("stringr")
library("pander")
library("lemon")
library("viridis")
library("ggthemes")
```

@@

correP <- function(df, mytitle, ...){
  require(ggplot2)
  require(ggcorrplot)

  p <- ggcorrplot(df, method = "square", type ='upper', 
                  outline.color = "black", colors = "white",
                  ggtheme = theme_minimal, 
                  lab = TRUE, lab_size = 12,
                  title = mytitle, show.legend = FALSE, 
                  tl.cex = 10)
  p <- p + theme(plot.title = element_text(size = 14, face = "bold.italic"))
  p      
}

g_rt <- correP(cor_rt, 'BAI Rt')
g_rc <- correP(cor_rc, 'BAI Rc')
g_rs <- correP(cor_rs, 'BAI Rs')
g_rte <- correP(cor_rte, 'EVI Rt')
g_rce <- correP(cor_rce, 'EVI Rc')
g_rse <- correP(cor_rse, 'EVI Rs')
